% status: 0
% chapter: TBD

\title{Big Data in Health Care}

\author{Hao Tian}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{School of Informatics, Computing and Engineering}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
  \country{USA}}
\email{tian4@indiana.edu}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{H. Tian.}


\begin{abstract}
The health care at today is an important topic in world wide, and as the population on the earth is growing, the health of human being need to be protected by more advanced method and technology. For tracking the health condition of citizens, each countries needs a complete medical care system, which could monitors the general health condition of people, and offers valuable information to medical services, such as hospitals, disease research institutions, even national security agencies. However, as the number of population on the earth now, the traditional methods and technologies cannot fully support the requirement of satisfying the health care for the most people.

For satisfying the purpose of severing all people with well functioning health care system, the cutting edge technology concepts - Big Data, brings a great generation for developing better health care systems. The basic concept of the Big Data is to process and analyse large mount of data, includes data mining, data visualization, and using machine learning knowledge to predict the future situation. With the large data amount in the health care fields, using the knowledges for processing Big Data is very helpful for dealing with issues in health care systems is facing today. 

This is paper discusses the Big Data technologies and application that are currently using in health care fields and the possible technologies that might be used in the future in order to improve the quality of health care. The serious illnesses, such as cancers, AIDS and other deadly diseases are also include in the discussion about the technologies concern with health care. 
\end{abstract} 

\keywords{I524, HID524, Big Data, Health Care, Medical Care, Data Mining, Cancer.}

\maketitle

\section{Introduction}
\subsection{Health care}
By starting this paper, we need to define what is health care. According to the definition from Merriam Webster dictionary: the health care is a efforts to maintain people in a healthy condition by trained and licensed medical professional~\cite{def_hc}. The healthy condition indicates both physical and mental status are healthy and well-being, they are basic factors which lead people to live in a happy life. 

Each countries in the world has different health care systems to maintain citizens health and protect citizens from getting diseases. The countries like Canada, the United Kingdom, and China have uniformed health care systems, they like national health care services which was provides to all the citizens~\cite{ca_hc, uk_hc, cn_hc}. The United States of America, as a developed country, has very unique status on health care: U.S. does not have a uniform health care system, and has no universal health care coverage for U.S. citizens until 2016~\cite{us_hc}. The free-market of medical care in U.S. brought great value to the U.S. economic growth~\cite{us_hccost}, but lacking of government management causes troubles for people to access the health care services with low cost~\cite{us_hcs}.

\section{Acknowledgments}
\begin{acks}

  The authors would like to thank Dr.~Gregor~von~Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

